Oasis or Mirage? \\ Trade Network Propagation of Deforestation

### 2024-01-02 paper/main.tex
modify section titles
add descriptive tables

\title{Oasis or Mirage? \\ Trade Network Propagation of Deforestation}
\author{Tomoki Nishiyama\footnote{Department of Economics, the University of Tokyo. \\ e-mail address: nishiyama-tomoki@g.ecc.u-tokyo.ac.jp \\ I thank Yasuyuki Sawada (an advisor of this thesis), Michihiro Kandori, and all the participants of their seminar for helpful discussion. I am also grateful to Shotaro Beppu, Yutao Chen, and Yuto Iwamoto for meaningful comments and supports.}}
\date{January 2024}
\maketitle

@@

As for the empirical method to examine propagation of a supply shock, I refer to recent growing literature of network analysis in economics. Acemoglu firstly introduces the analysis of how shock on an agent propagates to the other agents throughout network between agents. Based on this strand, various papers discuss how a shock to a specific firms affects the other firms that do not directly suffer from the shock through production supply chain. For example, \cite{barrot2016input} and \cite{carvalho2021supply} examine how shocks of the Eastern Japan Great Earthquake affects firms that are located far from the damaged area through their supply chain networks. I follow shift-share approach of \cite{huneeus2018production} to empirically show the network propagation effects of one country's pro-environmental policy on the other countries.\\

@@

\cite{acemoglu2012network}

@@

@@

\section{Conoclusion}

>>>>

\title{Oasis or Mirage? \\ Trade Network Propagation of Deforestation}
\author{Tomoki Nishiyama\footnote{Department of Economics, the University of Tokyo. \\ e-mail address: nishiyama-tomoki@g.ecc.u-tokyo.ac.jp \\ I thank Yasuyuki Sawada (a main advisory professor of this thesis), Michihiro Kandori, and all the participants of their seminar for helpful discussion. I am also grateful to Shotaro Beppu, Yutao Chen, and Yuto Iwamoto for meaningful comments and supports.}}
\date{January 2024}
\maketitle

@@

As for the empirical method to examine propagation of a supply shock, I refer to recent growing literature of network analysis in economics. \cite{acemoglu2012network} firstly introduces the analysis of how shock on an agent propagates to the other agents throughout network between agents. Based on this strand, various papers discuss how a shock to a specific firms affects the other firms that do not directly suffer from the shock through production supply chain. For example, \cite{barrot2016input} and \cite{carvalho2021supply} examine how shocks of the Eastern Japan Great Earthquake affects firms that are located far from the damaged area through their supply chain networks. I follow shift-share approach of \cite{huneeus2018production} to empirically show the network propagation effects of one country's pro-environmental policy on the other countries.\\

@@

@@

\begin{table}[htbp]
    \caption{Production of Forestry Goods and Usage of Logs}
    \centering
    \begin{tabular}{lcccc}
       \tabularnewline \midrule \midrule
       Dependent Variables:     & sawn                    & plywood                     & pulp                    & chip\\  
       Model:                   & (1)                     & (2)                         & (3)                     & (4)\\  
       \midrule
       \emph{Variables}\\
       conif\_domestic          & 0.2160$^{***}$          & 0.0567                      & 0.0378                  & -0.0339\\   
                                & (0.0651)                & (0.0514)                    & (0.0379)                & (0.2233)\\   
       conif\_imp               & 1.659$^{**}$            & 0.7917$^{**}$               & 0.3218$^{**}$           & 1.039$^{*}$\\   
                                & (0.6541)                & (0.3536)                    & (0.1473)                & (0.5378)\\   
       nonconif\_domestic       & -0.0033                 & -0.0903                     & 0.0080                  & 0.1929\\   
                                & (0.0879)                & (0.0607)                    & (0.0482)                & (0.1786)\\   
       nonconif\_trop\_imp      & 0.5227                  & 1.208                       & -0.3307                 & 2.094$^{*}$\\   
                                & (2.061)                 & (1.079)                     & (0.3494)                & (1.216)\\   
       nonconif\_nontrop\_imp   & -0.2427                 & -0.2589                     & 0.2553$^{**}$           & 0.7318\\   
                                & (0.6352)                & (0.2551)                    & (0.1219)                & (0.9474)\\   
       lag1\_gdp                & $2.46\times 10^{-6}$    & $1.86\times 10^{-6}$$^{*}$  & $2.83\times 10^{-7}$    & $-1.06\times 10^{-7}$\\    
                                & ($1.95\times 10^{-6}$)  & ($1.06\times 10^{-6}$)      & ($5.22\times 10^{-7}$)  & ($1.79\times 10^{-6}$)\\    
       \midrule
       \emph{Fixed-effects}\\
       area                     & Yes                     & Yes                         & Yes                     & Yes\\  
       as.factor(year)          & Yes                     & Yes                         & Yes                     & Yes\\  
       \midrule
       \emph{Fit statistics}\\
       Observations             & 2,812                   & 2,812                       & 1,869                   & 1,759\\  
       R$^2$                    & 0.97680                 & 0.96827                     & 0.98507                 & 0.86730\\  
       Within R$^2$             & 0.73537                 & 0.72402                     & 0.33070                 & 0.21385\\  
       \midrule \midrule
       \multicolumn{5}{l}{\emph{Clustered (area) standard-errors in parentheses}}\\
       \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
    \end{tabular}
 \end{table}

\textit{\textbf{Fact2:} Intensive margin (average value of export / import) accounts for more than half of the variation of countries' export and import}.
\begin{table}[H]
    \centering
    \caption{Cross-sectional Decomposition of Countries' Log Export Value}
    \begin{tabular}[t]{lcccccc}
    \toprule
    \textit{log type:} &  \multicolumn{2}{c}{Coniferous}&  \multicolumn{2}{c}{Non-conif Non-tropical}&  \multicolumn{2}{c}{Non-conif tropical}\\
    \midrule
      & (1) & (2) & (3) & (4) & (5) & (6)\\
      \textit{Dependent Var:}& Links & Average & Links & Average & Links & Average \\
    \midrule
    log(Export Value)  & \num{0.390}*** & \num{0.610}*** & \num{0.412}*** & \num{0.588}*** & \num{0.379}*** & \num{0.621}***\\
    & (\num{0.010}) & (\num{0.010}) & (\num{0.010}) & (\num{0.010}) & (\num{0.013}) & (\num{0.013})\\
   \midrule
   Num.Obs. & \num{95} & \num{95} & \num{120} & \num{120} & \num{102} & \num{102}\\
   R2 & \num{0.899} & \num{0.956} & \num{0.919} & \num{0.959} & \num{0.894} & \num{0.957}\\
   \bottomrule
   \multicolumn{7}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
   \end{tabular}
   \end{table}

\begin{table}[H]
    \centering
    \caption{Cross-sectional Decomposition of Countries' Log Import Value}
    \begin{tabular}[t]{lcccccc}
    \toprule
    \textit{log type:} &  \multicolumn{2}{c}{Coniferous}&  \multicolumn{2}{c}{Non-conif Non-tropical}&  \multicolumn{2}{c}{Non-conif tropical}\\
    \midrule
      & (1) & (2) & (3) & (4) & (5) & (6)\\
      \textit{Dependent Var:}& Links & Average & Links & Average & Links & Average \\
    \midrule
    log(Import Value) & \num{0.389}*** & \num{0.611}*** & \num{0.437}*** & \num{0.563}*** & \num{0.479}*** & \num{0.521}***\\
    & (\num{0.008}) & (\num{0.008}) & (\num{0.009}) & (\num{0.009}) & (\num{0.017}) & (\num{0.017})\\
   \midrule
   Num.Obs. & \num{141} & \num{141} & \num{136} & \num{136} & \num{80} & \num{80}\\
   R2 & \num{0.916} & \num{0.964} & \num{0.923} & \num{0.952} & \num{0.882} & \num{0.899}\\
   \bottomrule
   \multicolumn{7}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
   \end{tabular}
   \end{table}

   \begin{table}[H]
    \caption{Cross-sectional Gravity Equation of Log Export Value}
    \centering
    \begin{tabular}{lccc}
       \tabularnewline \midrule \midrule
       Dependent Variable: & \multicolumn{3}{c}{log(Export Value)}\\
       \midrule
       \textit{log type: } & Coniferous & Non-conif Non-tropical & Non-conif Tropical\\
       Model:                             & (1)            & (2)            & (3)\\  
       \midrule
       \emph{Variables}\\
       log(distw)                         & -1.916$^{***}$ & -1.226$^{***}$ & -0.6735$^{***}$\\   
       & (0.1864)       & (0.1215)       & (0.0907)\\   
        \midrule
        \emph{Fixed-effects}\\
        year-exporter  & Yes            & Yes            & Yes\\  
        year-importer   & Yes            & Yes            & Yes\\  
        \midrule
        \emph{Fit statistics}\\
        Observations                       & 17,124         & 22,695         & 9,494\\  
        R$^2$                              & 0.51745        & 0.47173        & 0.60015\\  
        Within R$^2$                       & 0.21867        & 0.15971        & 0.06400\\  
        \midrule \midrule
        \multicolumn{4}{l}{\emph{Clustered (exporter country and importer country) standard-errors in parentheses}}\\
        \multicolumn{4}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
    \end{tabular}
 \end{table}

@@

\section{Conclusion}
